### 2019-10-04 submission/manuscript.Rmd
Add abstract

## Abstract
250 words

## Importance
150 words

>>>>

## Abstract
More than 10 years ago, we published the manuscript describing the mothur software package in *Applied and Environmental Microbiology*. Our goal was to create a comprehensive package that allowed users to analyze amplicon sequence data using the most robust methods available. Looking back, it is clear that mothur continues to provide this service to the microbial ecology community as it has helped to lead the community through the ongoing sequencing revolution. Beyond its success and impact on the field, mothur's development exposed a series of observations that are generally translatable across science. Although it is easy to criticize choices that were made 10 years ago through a modern lens, all science is done in the context of prevailing ideas and available technologies. If we were to wait for all of the possible limitations to be solved before proceeding, science would stall. Even preceding the development of mothur, it was necessary to address the most important problems and work backwards to other problems that limited access to robust sequence analysis tools. At the same time, we strive to expand mothur's capabilities in a data-driven manner to incorporate new ideas and accommodate changes in data and desires of the research community. As we develop mothur, we first consider the needs of my research group. In hindsight, we appreciate that our needs are representative of the broader community's. It has been edifying to see the benefit that a simple set of tools can bring to so many other researchers.

### 2019-10-04 submission/manuscript.tex
Add abstract

250 words

\hypertarget{importance}{%
\subsection{Importance}\label{importance}}

150 words

>>>>

More than 10 years ago, we published the manuscript describing the
mothur software package in \emph{Applied and Environmental
Microbiology}. Our goal was to create a comprehensive package that
allowed users to analyze amplicon sequence data using the most robust
methods available. Looking back, it is clear that mothur continues to
provide this service to the microbial ecology community as it has helped
to lead the community through the ongoing sequencing revolution. Beyond
its success and impact on the field, mothur's development exposed a
series of observations that are generally translatable across science.
Although it is easy to criticize choices that were made 10 years ago
through a modern lens, all science is done in the context of prevailing
ideas and available technologies. If we were to wait for all of the
possible limitations to be solved before proceeding, science would
stall. Even preceding the development of mothur, it was necessary to
address the most important problems and work backwards to other problems
that limited access to robust sequence analysis tools. At the same time,
we strive to expand mothur's capabilities in a data-driven manner to
incorporate new ideas and accommodate changes in data and desires of the
research community. As we develop mothur, we first consider the needs of
my research group. In hindsight, we appreciate that our needs are
representative of the broader community's. It has been edifying to see
the benefit that a simple set of tools can bring to so many other
researchers.
